sensiAnPaper1All

### 2020-11-11 inst/documents/linkage_dis_2017.Rmd
rerun linkage dis plots

---
  title: "linkage disequilibrium"
  output: pdf_document
  #output: word_document
  author: "Andy South"
  date: "`r Sys.Date()`"
---

@@

```{r Fig8, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left'}

>>>>

---
  title: "linkage disequilibrium"
  output: pdf_document
  #output: word_document
  author: "Andy South"
  date: "originally from 2017, rerun:`r Sys.Date()`"
---

@@

```{r Fig8, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', warning=FALSE}
